Biden Projected to Win the 2024 US Presidential Elections

### 2024-03-16 paper/paper.qmd
Preamble updates, citations for all packages used added and poststrat sim added

library(rstan)
library(tidyverse)
library(arrow)
library(dplyr)
library(knitr)
library(ggplot2)
library(gutenbergr)
library(haven)
library(labelled)
library(modelsummary)
library(rstanarm)
library(tidybayes)
library(broom.mixed)
library(here)
library(kableExtra)

# read the datasets and model
poststrat_data <- arrow::read_parquet(file = here("data/analysis_data/poststrat_data.parquet"))
survey_data <- arrow::read_parquet(file = here("data/analysis_data/survey_data.parquet"))
us_election_model <- readRDS(file = here("models/single_bay.rds"))

state_vote_for_biden <- read.csv(here("data/poststratified/state_vote_for_biden.csv"))
age_vote_for_biden <- read.csv(here("data/poststratified/age_vote_for_biden.csv"))
sex_vote_for_biden <- read.csv(here("data/poststratified/sex_vote_for_biden.csv"))
general_data <- read.csv(here("data/poststratified/general_vote_for_biden.csv"))

@@

For this analysis, we have used two datasets. The datasets were cleaned and analysed using the statistical programming software R [@citeR] along with the help tidyverse [@citeTidyverse], knitr [@citeKnitr], ggplot2 [@citeGgplot], here [@citeHere], ADD MORE

@@

```{r}
head(survey_data)
```

## Poststratification dataset
Here is a glimpse of the poststratification data set used
```{r}
head(poststrat_data)
```

>>>>

# install.packages("broom.mixed")
# install.packages("tidyverse")
# install.packages("arrow")
# install.packages("dplyr")
# install.packages("knitr")
# install.packages("ggplot2")
# install.packages("modelsummary")
# install.packages("here")
# install.packages("kableExtra")

library(broom.mixed)
library(tidyverse)
library(arrow)
library(dplyr)
library(knitr)
library(ggplot2)
library(modelsummary)
library(here)
library(kableExtra)

# Read the datasets and model
poststrat_data <- arrow::read_parquet(file = here("data/analysis_data/poststrat_data.parquet"))
survey_data <- arrow::read_parquet(file = here("data/analysis_data/survey_data.parquet"))
us_election_model <- readRDS(file = here("models/single_bay.rds"))

# Read the post-stratified data
state_vote_for_biden <- read.csv(here("data/poststratified/state_vote_for_biden.csv"))
age_vote_for_biden <- read.csv(here("data/poststratified/age_vote_for_biden.csv"))
sex_vote_for_biden <- read.csv(here("data/poststratified/sex_vote_for_biden.csv"))
general_data <- read.csv(here("data/poststratified/general_vote_for_biden.csv"))

@@

For this analysis, we have used two datasets. The datasets were cleaned and analysed using the statistical programming software R [@citeR] along with the help tidyverse [@citeTidyverse], knitr [@citeKnitr], ggplot2 [@citeGgplot], here [@citeHere], dplyr [@citeDplyr], arrow [@citeArrow], rstanarm [@citeRstanarm], broom.mixed [@citeBroomMixed], modelsummary [@citeModelSummary] and kableExtra [@citeKableExtra].

@@

```{r}
#| echo: false
#| warning: false
#| message: false

head(survey_data)
```

## Poststratification dataset
Here is a glimpse of the poststratification data set used
```{r}
#| echo: false
#| warning: false
#| message: false

head(poststrat_data)
```
